Get basic stats for seedling censuses & make figures

Tyler L. McIntosh
CU Boulder CIRES Earth Lab
Last updated: 9/21/23

This script uses the following naming conventions wherever possible:
 lowerCamelCase for variables
 period.separated for functions
 underscore_separated for files

```{r, echo = FALSE, warning = FALSE}
# SETUP ----
## Libraries ----

#Check the required libraries and download if needed
list.of.packages <- c("tidyverse", "terra", "sf", "mapview", "here", "landscapemetrics", "tictoc", "flextable")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

#Load
library(tidyverse) #Tidyverse!
library(terra) #New raster data package, documentation pdf here: https://cran.r-project.org/web/packages/terra/terra.pdf
library(sf) #New vector data package
library(mapview) #For quick interactive mapping
library(here) #Relative path best practices
library(landscapemetrics) #Fragstats for R
library(tictoc) #time running of processes
library(flextable)

## Clean workspace & set up environment ----
rm(list=ls()) #Ensure empty workspace if running from beginning
here() #Check here location
#OR
#setwd() #Set working directory directly
options(digits = 2) #Set standard decimal print output
options(scipen = 999) #Turn scientific notation on and off (0 = on, 999 = off)
```


Create a table for UAS Specifications & flight parameters:

```{r}


`Parameter Type` <- c("UAS Specifications",
                      "UAS Specifications",
                      "UAS Specifications",
                      "UAS Specifications",
                      "UAS Specifications",
                      "UAS Specifications",
                      "UAS Flight Parameters",
                      "UAS Flight Parameters",
                      "UAS Flight Parameters",
                      "UAS Flight Parameters",
                      "UAS Flight Parameters",
                      "UAS Flight Parameters",
                      "UAS Flight Parameters")
`UAS Flight Parameter`<- c("Vehicle",
                            "Payload",
                            "Sensor",
                           "Lens",
                           "ISO Range",
                           "Shutter",
                           "Flight planning software",
                            "Altitude",
                            "Along track overlap",
                            "Across track overlap",
                            "Flight speed",
                            "Terrain follow use",
                            "Flight pattern")
`Parameter Details` <- c("DJI Phantom 4 Pro",
                "Integrated off-the-shelf RGB camera",
                "1 inch CMOS sensor, 20M effective pixels",
                "FOV 84° 8.8 mm/24 mm (35 mm format equivalent) f/2.8 - f/11 auto focus at 1 m - ∞",
                "100-3200 (Auto)",
                "Electronic & Mechanical shutter",
                "Map Pilot Pro",
                "100m Above Ground Level (AGL)",
                "85%",
                "85%",
                "6.0 m/s",
                "Activated: Elevation profile USGS 30m SRTM",
                "Grid mission")

uas_table <- cbind(`Parameter Type`, `UAS Flight Parameter`, `Parameter Details`) %>% as.data.frame()

ft_uas <- flextable::flextable(uas_table) %>%
  flextable::set_table_properties(layout = "fixed") %>%
  flextable::width(j = 1, width = 1, unit = "in") %>%
  flextable::width(j = 2, width = 1.5, unit = "in") %>% 
  flextable::width(j = 3, width = 3.5, unit = "in") %>% 
  flextable::merge_at(i = 1:6, j = 1) %>%
  flextable::merge_at(i = 7:13, j = 1) %>%
  flextable::theme_vanilla() %>%
  line_spacing(space = 1.5, part = "all")
ft_uas

save_as_image(ft_uas, path = here::here("figs", "UAS_params.jpeg"))

```

Create a figure showing the fires of interest and location of census plots:

```{r}
mtbs <- sf::st_read(here::here('data', 'derived', 'filtered', 'ponderosa_usfs_200.gpkg'))

selectedFires <- mtbs %>% 
  filter(event_name == 'HAYMAN' |
           event_name == 'SCHOONOVER' |
           event_name == 'BIG ELK' |
           event_name == 'HIGH MEADOWS')

plot(selectedFires$geom)


```

```{r}
#Read data
censusPolygons <- sf::st_read(here::here('data', 'career_census_23_polygons_7_5_23_FINAL.geojson'))

mapview(censusPolygons)

```

