---
title: "VictoriaFireSummaryScript: TM Edits"
author: "Victoria Scholl & Tyler McIntosh"
date: '2022-04-26'
output: html_document
---
```{r setup, include=FALSE}
#Set global RMarkdown
knitr::opts_chunk$set(echo = FALSE)
```

Create a table summarizing data layers within each MTBS fire. 
Layers were assembled and reduced in Google Earth Engine, then the summary file exported to Google Drive.
Downloaded the summary table locally from Google Drive, then ran this script to visualize and explore the data.

UPDATE: This script has been updated to filter for only ponderosa-dominated fire events (NOW COMMENTED OUT: with greater than 50% GEDI coverage). Additional metrics have been added, such as % USFS land, fire severity homogeneity, and burn severity amounts. Code hidden for ease of reading.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
#Clear workspace
rm(list = ls())

#Set working directory
here::i_am("VictoriaFireSummaryScript.rmd")

# Install packages
library(sf) 
library(here)
library(dplyr) 
library(kableExtra)
library(ggplot2)
library(tidyr)
library(ggrepel)
library(landscapemetrics)

here::here()
```

```{r, message=FALSE, warning=FALSE}
# read shapefile where each row describes one fire 


# MTBS fires on USFS land, 200km from NIWO, within NEON domain 13
#      Fig 1 height: 8, Fig 4 height: 10
#fire_filename <- here::here("data/fire_stats_test.geojson")

# MTBS fires on USFS land, within the Southern Rockies EPA Level III ecoregion
#      Fig 1 height: 16, Fig 4 height: 16
#fire_filename <- here::here("data/fires_sRockiesEcoregion_USFS.geojson")

# MTBS fires within the Southern Rockies EPA Level III ecoregion
#      Fig 1 height: 24, Fig 4 height: 30
#fire_filename <- here::here("data/fires_sRockiesEcoregion.geojson")

# MTBS fires on USFS land, 200km from NIWO
#fire_filename <- here::here("data/fires_MTBS_local.geojson")

# FIRED fires on USFS land, 200km from NIWO
# Is there a way to get a fire's name from the FIRED data? 
#fire_filename <- here::here("data/fires_FIRED_local.geojson")

# MTBS fires <200km from NIWO, with forest cover, addding in GEDI cover 
fire_filename <- here::here("data/fires_stats_20210414.geojson")



# NAME OF CURRENT DATA SET OR ITERATION
# used to name output figures
out_label <- "MTBS_local_with_GEDI"



# Set figure height and width for Rmd html output
figHeight <- 10
figWidth <- 10



# read the fire data
fire_df <- sf::st_read(fire_filename)

# adjust the data type and/or precision of some fields
fire_df$id <- as.character(fire_df$id)     # Fire name 
fire_df$Acres <- as.integer(fire_df$Acres) # Fire size [acres]
fire_df$gedi_coverage <- round(as.numeric(as.character(fire_df$gedi_coverage)) * 100, digits = 1) # Percent GEDI pixels in fire perimeter
fire_df$lodgepole <- round(as.numeric(as.character(fire_df$lodgepole)) * 100, digits = 1)     # Percent lodgepole 
fire_df$ponderosa <- round(as.numeric(as.character(fire_df$ponderosa)) * 100, digits = 1)     # Percent ponderosa pine 
fire_df$spruceFir <- round(as.numeric(as.character(fire_df$spruceFir)) * 100, digits = 1)     # Percent spruce/fir 
fire_df$disturbed_burned <- round(as.numeric(as.character(fire_df$disturbed_burned)) * 100, digits = 1) # Percent burned
fire_df$disturbed_unspecific <- round(as.numeric(as.character(fire_df$disturbed_unspecific)) * 100, digits = 1) # Percent disturbed
#fire_df$disturbed_logged <- round(as.numeric(as.character(fire_df$disturbed_logged)) * 100, digits = 1)
#fire_df$regenerating_disturbed <- round(as.numeric(as.character(fire_df$regenerating_disturbed)) * 100, digits = 1)
#fire_df$regenerating_harvested <- round(as.numeric(as.character(fire_df$regenerating_harvested)) * 100, digits = 1)
```


```{r}
# how many fires in this data set? 
message("# of fires in dataset: ")
message(nrow(fire_df))

# create output directory for figures
if(!dir.exists(here::here("figures"))){
  dir.create(here::here("figures"))
}
```


```{r, message=FALSE, warning=FALSE, results=FALSE}
# create a table to summarize attributes of interest per fire 
fire_table <- as.data.frame(fire_df) %>% 
  # select columns of interest
  dplyr::select(Fire_Name, Year, Acres, gedi_coverage, lodgepole, ponderosa, spruceFir, disturbed_burned, disturbed_unspecific, 
                #disturbed_logged, regenerating_disturbed, regenerating_harvested
                ) %>%
  # reorder the rows based on multiple variables 
  dplyr::arrange(desc(gedi_coverage), desc(lodgepole), desc(ponderosa), desc(spruceFir), desc(disturbed_burned)) %>%
  # rename the columns for interpretation
  dplyr::rename("Fire Name" = Fire_Name, 
                "Year" = Year,
                "Acres" = Acres,
                "GEDI %" = gedi_coverage,
                "Lodgepole %" = lodgepole,
                "Ponderosa %" = ponderosa,
                "Spruce Fir %" = spruceFir,
                "Disturbed Burned %" = disturbed_burned,
                "Disturbed Unspecified %" = disturbed_unspecific,
                #"Disturbed Logged %" = disturbed_logged,
                #"Regenerating Disturbed %" = regenerating_disturbed,
                #"Regenerating Harvested %" = regenerating_harvested
                ) 

# add a categorical column with dominant forest type 
temp <- fire_df %>% 
  dplyr::select(Fire_Name, lodgepole, ponderosa, spruceFir) %>% 
  tidyr::gather(major_forest_type, forest_percent, lodgepole:spruceFir) %>% 
  dplyr::group_by(Fire_Name) %>% 
  dplyr::slice(which.max(forest_percent)) %>% 
  dplyr::select(Fire_Name, major_forest_type) %>% 
  st_set_geometry(NULL)
fire_df <- fire_df %>% 
  dplyr::left_join(temp)
remove(temp)



kableExtra::kable(fire_table) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", 
                            full_width = F, 
                            position = "left")

```


```{r}
# count number of fires with each dominant forest type 
kableExtra::kable(table(fire_df$major_forest_type),
                  col.names = c("Dominant forest type", "# of fire events")) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", 
                            full_width = F, 
                            position = "left")
```

```{r, message=FALSE}
# subset to only include ponderosa & GEDI > =50, create table
subset_fire_df <- fire_df %>% filter(major_forest_type == 'ponderosa') #  %>% filter(gedi_coverage >= 50)

# create a table to summarize attributes of interest per fire 
subset_fire_table <- as.data.frame(subset_fire_df) %>% 
  # select columns of interest
  dplyr::select(Fire_Name, Fire_ID, Year, Acres, gedi_coverage, lodgepole, ponderosa, spruceFir, disturbed_burned, disturbed_unspecific, 
                #disturbed_logged, regenerating_disturbed, regenerating_harvested
                ) %>%
  # reorder the rows based on multiple variables 
  dplyr::arrange(desc(gedi_coverage), desc(lodgepole), desc(ponderosa), desc(spruceFir), desc(disturbed_burned)) %>%
  # rename the columns for interpretation
  dplyr::rename("Fire Name" = Fire_Name, 
                "Year" = Year,
                "Acres" = Acres,
                "GEDI %" = gedi_coverage,
                "Lodgepole %" = lodgepole,
                "Ponderosa %" = ponderosa,
                "Spruce Fir %" = spruceFir,
                "Disturbed Burned %" = disturbed_burned,
                "Disturbed Unspecified %" = disturbed_unspecific,
                #"Disturbed Logged %" = disturbed_logged,
                #"Regenerating Disturbed %" = regenerating_disturbed,
                #"Regenerating Harvested %" = regenerating_harvested
                ) 

# add a categorical column with dominant forest type 
temp <- subset_fire_df %>% 
  dplyr::select(Fire_Name, lodgepole, ponderosa, spruceFir) %>% 
  tidyr::gather(major_forest_type, forest_percent, lodgepole:spruceFir) %>% 
  dplyr::group_by(Fire_Name) %>% 
  dplyr::slice(which.max(forest_percent)) %>% 
  dplyr::select(Fire_Name, major_forest_type) %>% 
  st_set_geometry(NULL)
subset_fire_df <- subset_fire_df %>% 
  dplyr::left_join(temp)
remove(temp)
```
```{r, message=FALSE}

#Add fire metrics to fires of interest
firemetrics <- read.csv(file = here('data', 'FireMetrics.csv'))
firemetrics <- firemetrics %>% dplyr::mutate(Fire_ID = toupper(FireID), FireID = NULL) %>%
  dplyr::mutate(ShannonDiv = round(ShannonDiv, 2)) %>% dplyr::mutate(ShannonEven = round(ShannonEven, 2)) %>% dplyr::mutate(PatchDiversity = round(PatchDiversity, 2)) %>%
  dplyr::mutate(EdgeDensity = round(EdgeDensity, 2)) #Round metrics
firemetrics <- firemetrics %>% dplyr::mutate(PercUnburned = round(100*(UnburnedPix / (UnburnedPix + LowBurnPix + ModerateBurnPix + HighBurnPix + IncreasedGreenPix + NonProcessPix)))) %>%
  dplyr::mutate(PercLowBurn = round(100*(LowBurnPix / (UnburnedPix + LowBurnPix + ModerateBurnPix + HighBurnPix + IncreasedGreenPix + NonProcessPix)))) %>%
  dplyr::mutate(PercModerateBurn = round(100*(ModerateBurnPix / (UnburnedPix + LowBurnPix + ModerateBurnPix + HighBurnPix + IncreasedGreenPix + NonProcessPix)))) %>%
  dplyr::mutate(PercHighBurn = round(100*(HighBurnPix / (UnburnedPix + LowBurnPix + ModerateBurnPix + HighBurnPix + IncreasedGreenPix + NonProcessPix)))) %>%
  dplyr::mutate(PercIncreasedGreenPix = round(100*(IncreasedGreenPix / (UnburnedPix + LowBurnPix + ModerateBurnPix + HighBurnPix + IncreasedGreenPix + NonProcessPix)))) %>%
  dplyr::mutate(PercNonprocessPix = round(100*(NonProcessPix / (UnburnedPix + LowBurnPix + ModerateBurnPix + HighBurnPix + IncreasedGreenPix + NonProcessPix))))
subset_fire_df <- subset_fire_df %>% dplyr::left_join(firemetrics, by = 'Fire_ID', suffix = c("_original", "_new"))
#subset_fire_table <- subset_fire_table %>% dplyr::left_join(firemetrics, by = 'Fire_ID', suffix = c("_original", "_new"))
subset_fire_table <- subset_fire_table %>% dplyr::arrange(desc(Year), desc('Gedi %'))

perc_USFS <- read.csv(file = here('data', 'Fires_PercUSFS.csv')) %>% dplyr::mutate(PercUSFS = round(PercUSFS, 1)) %>% dplyr::select(Fire_ID, PercUSFS)
subset_fire_table <- subset_fire_table %>% dplyr::left_join(perc_USFS, by = 'Fire_ID', suffix = c("_original", "_new"))
subset_fire_df <- subset_fire_df %>% dplyr::left_join(perc_USFS, by = 'Fire_ID', suffix = c("_original", "_new"))


# subset_fire_table <- subset_fire_table %>%
#   dplyr::select(-Fire_ID, -UnburnedPix, -LowBurnPix, -ModerateBurnPix, -HighBurnPix, -IncreasedGreenPix, -NonProcessPix, -'Disturbed Burned %', -'Disturbed Unspecified %')
subset_fire_table <- subset_fire_table %>%
   dplyr::select(-Fire_ID, -'Disturbed Burned %', -'Disturbed Unspecified %') %>% dplyr::rename("USFS %" = PercUSFS)

#Calculate USFS percent groups & GEDI percent groups
subset_fire_df <- subset_fire_df %>% dplyr::mutate(USFSGroup = ifelse(PercUSFS >= 50, '>=50% USFS', ifelse(PercUSFS <= 30, '<=30% USFS', '30-50% USFS')))
subset_fire_df <- subset_fire_df %>% dplyr::mutate(GEDIGroup = ifelse(gedi_coverage >= 50, '>=50% GEDI', '<50% GEDI'))

```
Note that a substantial part of the Hayden Pass fire is in a wilderness area, making it impossible for us to fly drones over that part of the fire. However, this part of the fire would likely be difficult to get equipment into, so we probably wouldn't be flying there anyway due to the effort involved.

```{r}

#Generate outputs to file
message("{Generating outputs}")
message("PONDEROSA DOMINATED FIRES w/ GEDI >= 50% coverage")
message("Number of fires:")
message(nrow(subset_fire_df))


kableExtra::kable(subset_fire_table) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", 
                            full_width = F, 
                            position = "left") %>%
  kableExtra::column_spec(1:2, color = "white", background = spec_color(subset_fire_table$Year, end = 0.7))
```



# Explore the fire data


## Map 

```{r, fig.height=9, fig.width=9, message=FALSE, warning=FALSE}
library(leaflet)
library(rgdal)
library(geojsonio)

# read geojson file for mapping with leaflet
#fire_gjson <- rgdal::readOGR(fire_filename)
fire_gjson <- st_read(fire_filename)


#CHANGE TO BE ONLY PONDEROSA & ONLY GEDI >=50%
fire_df_orig <- fire_df
fire_df <- subset_fire_df
fire_gjson_orig <- fire_gjson
fire_gjson <- fire_gjson %>% filter(id %in% fire_df$id)# %>% filter(gedi_coverage >= 0.50)

# add a column with fire perimeter centroid point locations for map labels
fire_df$centroid_lon <- NA
fire_df$centroid_lat <- NA
fire_df$centroid_label <- NA
for (i in 1:nrow(fire_df)){
  # create popup label using fire name and year
  content <- paste(sep = "<br/>",
    fire_df$Fire_Name[i], fire_df$Year[i], "Percent of fire in USFS land: ", fire_df$PercUSFS[i], "Acres: ", fire_df$Acres[i])
  #print(content)
  fire_df$centroid_label[i] <- content
  
  # get lon, lat coordinates of geometry centroid  
  fire_df$centroid_lon[i] <- st_centroid(fire_df$geometry[i])[[1]][1]
  fire_df$centroid_lat[i] <- st_centroid(fire_df$geometry[i])[[1]][2]
}


# color palette
pal <- colorNumeric(
  palette = "viridis",
  domain = fire_gjson$Year
)

# map the fire polygons
map <- leaflet(fire_gjson) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 0.7,
    color = ~pal(Year), group = "MTBS fires"
  ) %>%
  addLegend("bottomright", pal = pal, values = ~Year,
    title = "Fire Year",
    # get rid of the comma in years (1,990 becomes 1990) for legend entries
    labFormat = labelFormat(big.mark = ''),
    opacity = 1
  ) %>% 
  # set base map type
  addProviderTiles(providers$CartoDB.Positron, group = "Carto") %>%
  addProviderTiles(providers$Stamen.Terrain, group = "Stamen")

# Icons 
icons <- makeAwesomeIcon(
  icon = "fire",
  iconColor = "gray",
  library = "fa",
  markerColor = "gray"
)


# Add Fire Name popup labels to each polygon centroid
  map <- map %>%
    #addMarkers(lng = fire_df$centroid_lon,
    addAwesomeMarkers(lng = fire_df$centroid_lon,
               lat = fire_df$centroid_lat,
               icon=icons,
               popup = fire_df$centroid_label) %>% 
    addLayersControl(baseGroups = c("Carto", "Stamen"), 
                   overlayGroups = c("MTBS fires"))  


# display map
map

```





```{r fig1, fig.height = figHeight, fig.width = figWidth, include = FALSE}
## Fire timeline
#Fire timeline showing fire years and relative sizes.

# calculate minimum and maximum fire years
year_min <- min(fire_df$Year)
year_max <- max(fire_df$Year)

# set forest type colors for the figures
                       # lodgepole  ponderosa  spruceFir
#forest_type_colors <- c("#005a32", "#74c476", "#e5f5e0") 
forest_type_colors <- c("#04663B", "#41ab5d", "#c7e9c0")


# reorder the rows based on year
fire_df <- fire_df %>% 
  dplyr::arrange(desc(Year)) 

# calculate point size - scaled relatively by fire size
tmp <- log(fire_df$Acres / max(fire_df$Acres))
tmp <- tmp + abs(min(tmp)) + 1.25

# create timeline figure 
ggplot(fire_df) + 
  geom_point(aes(x = reorder(Fire_Name, Year), y = Year, 
                 # color points based on dominant forest type
                 fill = major_forest_type), 
             # add a black outline around each point
             color = "black", shape=21, 
             # size of each point, thickness of outline
             size = tmp, 
             stroke = 0.3) + 
  scale_y_continuous(breaks = seq(year_min, year_max, by = 4)) + 
  labs(title = "Fire Event Timeline", y = "Year", x = "Fire Name\n",
       fill = "Dominant forest type") + 
  # Put fire name on Y axis, year on X axis
  coord_flip() + 
  # set the point fill colors using hex codes 
  # scale_fill_manual(values = forest_type_colors,
  #                   labels = c("Lodgepole pine", "Ponderosa pine", "Spruce/Fir")) + 
  # set the point size in legend 
  guides(fill = guide_legend(override.aes = list(size=4))) + 
  # clean theme for plot with white background
  theme_bw() 

# Save figure to file
ggsave(filename = (here::here(file.path("figures",paste0(out_label,"-fire_timeline.png")))),
       width = 8, height = 6)
```


## Fire year histograms

Three histograms, one showing specific years of the fires, and two others showing decadal bins (either '00-'10 etc or '05-'15 etc)

```{r warning=FALSE, fig.align="center"}



hist_year_title <- paste("Histogram: Fire Years,", year_min, "-", year_max)

# create histogram, fire count per year.
# color the bars based on the dominant forest type of each fire event. 

ggplot(fire_df, aes(x=Year, fill = major_forest_type)) + 
  geom_histogram(binwidth=1, color="black", 
                 # set the outline thickness and bar transparency. 
                 size = 0.2, alpha=0.9) + 
  labs(title = hist_year_title, y = "Count", fill = "Dominant forest type") + 
  # x axis label years from min to max year in increments of 4
  scale_x_continuous(breaks = seq(1980, 2020, by = 5)) + 
  # set color scale of the dominant forest types
  # scale_fill_manual(values= forest_type_colors,
  #                   labels = c("Lodgepole pine", "Ponderosa pine", "Spruce/Fir")) + 
  theme_bw()

# Save figure to file
ggsave(filename = (here::here(file.path("figures",paste0(out_label,"-fire_hist_years1.png")))),
       width = 7, height = 5)

ggplot(fire_df, aes(x=Year, fill = major_forest_type)) + 
  geom_histogram(binwidth=10, color="black", 
                 # set the outline thickness and bar transparency. 
                 size = 0.2, alpha=0.9) + 
  labs(title = hist_year_title, y = "Count", fill = "Dominant forest type") + 
  # x axis label years from min to max year in increments of 4
  scale_x_continuous(breaks = seq(1980, 2020, by = 5)) + 
  # set color scale of the dominant forest types
  # scale_fill_manual(values= forest_type_colors,
  #                   labels = c("Lodgepole pine", "Ponderosa pine", "Spruce/Fir")) + 
  theme_bw()

# Save figure to file
ggsave(filename = (here::here(file.path("figures",paste0(out_label,"-fire_hist_years2.png")))),
       width = 7, height = 5)


ggplot(fire_df, aes(x=Year, fill = major_forest_type)) + 
  geom_histogram(binwidth=10, color="black", 
                 # set the outline thickness and bar transparency. 
                 size = 0.2, alpha=0.9, breaks = c(1980, 1990, 2000, 2010, 2020)) + 
  labs(title = hist_year_title, y = "Count", fill = "Dominant forest type") + 
  # x axis label years from min to max year in increments of 4
  scale_x_continuous(breaks = seq(1980, 2020, by = 5)) + 
  # set color scale of the dominant forest types
  # scale_fill_manual(values= forest_type_colors,
  #                   labels = c("Lodgepole pine", "Ponderosa pine", "Spruce/Fir")) + 
  theme_bw()

# Save figure to file
ggsave(filename = (here::here(file.path("figures",paste0(out_label,"-fire_hist_years3.png")))),
       width = 7, height = 5)
```

## Fire size histogram

```{r message=FALSE, warning=FALSE, fig.align="center", include=FALSE}
# color the bars based on the dominant forest type of each fire event. 
           # convert from Acres to Hectares? * 0.404686
ggplot(fire_df, aes(x = Acres * 0.404686)) + 
  geom_histogram(aes(fill = major_forest_type), color="black", 
                 # set the outline thickness and bar transparency. 
                 size = 0.2, alpha=0.9) + 
  labs(title = "Histogram: Fire Size", y = "Count", x = "Size [Hectares]",
       fill = "Dominant forest type") + 
  # set color scale of the dominant forest types
  # scale_fill_manual(values = forest_type_colors,
  #                   labels = c("Lodgepole pine", "Ponderosa pine", "Spruce/Fir")) + 
  theme_bw()

# Save figure to file
ggsave(filename = (here::here(file.path("figures",paste0(out_label,"-fire_hist_size.png")))),
       width = 7, height = 5)
```


```{r message=FALSE, warning=FALSE, fig.align="center"}
ggplot(fire_df, aes(x = Acres * 0.404686)) + 
  geom_histogram(aes(fill = major_forest_type), color="black", 
                 # set the outline thickness and bar transparency. 
                 size = 0.2, alpha=0.9, breaks = c(seq(0, 10000, 1000))) + 
  labs(title = "Fire Size Histogram: 1000 hectare bins", y = "Count", x = "Size [Hectares]",
       fill = "Dominant forest type") + 
  # set color scale of the dominant forest types
  # scale_fill_manual(values = forest_type_colors,
  #                   labels = c("Lodgepole pine", "Ponderosa pine", "Spruce/Fir")) + 
  theme_bw()

# Save figure to file
ggsave(filename = (here::here(file.path("figures",paste0(out_label,"-fire_hist_size2.png")))),
       width = 7, height = 5)
```

## Fire size as a function of year 
With percent of fire inside USFS lands & GEDI coverage

```{r, fig.height = 10, fig.width = 10}
ggplot(fire_df, aes(x=Year, y=Acres * 0.404686 , 
                    log="y", label = Fire_Name)) + 
  geom_point(aes(# color points
                 color = USFSGroup, shape = GEDIGroup), 
             # size of each point, thickness of outline
             size = 4, stroke = 0.5) + 
  labs(title = "Fire size vs year", 
       y = "Hectares [log transformed]", 
       fill = "Fire area within USFS land",
       shape = "GEDI Coverage") + 
  # log transform the y axis to space out the points more 
  scale_y_continuous(trans='log2') + 
  scale_x_continuous(breaks = seq(year_min, year_max, by = 4)) + 
  # scale_fill_manual(values = forest_type_colors,
  #                   labels = c("Lodgepole pine", "Ponderosa pine", "Spruce/Fir")) + 
  # add Fire Name labels
  geom_label_repel(aes(label = Fire_Name),
                   box.padding   = 0.35, 
                   point.padding = 0.5,
                   segment.color = 'grey50') + 
  
  theme_bw() + 
  # font size
  theme(axis.text.y = element_text(size=16),
        axis.title.y = element_text(size=16),
        axis.text.x = element_text(size=16),
        axis.title.x = element_text(size=16),
        # move the legend to the top of the figure
        legend.position="top") 

# Save figure to file
ggsave(filename = (here::here(file.path("figures",paste0(out_label,"-fire_size_vs_year_scatterplot.png")))),
       width = 7, height = 9)
```


## Severity data

Severity proportions and homogeneity metrics for selected fires, based on MTBS-established severity classes


SUMMARY GRAPHS

```{r, echo = FALSE, warning = FALSE}

fire_df <- fire_df %>% dplyr::mutate("ShannonDivScale" = scale(ShannonDiv)) %>%
  dplyr::mutate("ShannonEvenScale" = scale(ShannonEven)) %>%
  dplyr::mutate("PatchDiversityScale" = scale(PatchDiversity)) %>%
  dplyr::mutate("EdgeDensityScale" = scale(EdgeDensity))

#Make graph of scaled homogeneity
homogeneity <- fire_df %>% dplyr::select(Fire_Name, ShannonDivScale, ShannonEvenScale, PatchDiversityScale, EdgeDensityScale) %>%
  as.data.frame() %>% dplyr::select(-geometry) %>% gather(key="Metric", value="Value", 2:5)

ggplot(homogeneity, aes(fill = Metric, x=Fire_Name, y=Value)) + geom_col(position="dodge") + coord_flip() + labs(title = "Fires by standardized severity homogeneity metrics")



#Make percentage graph of severities
severe <- fire_df %>% dplyr::select(Fire_Name, PercUnburned, PercLowBurn, PercModerateBurn, PercHighBurn) %>%
  as.data.frame() %>% dplyr::select(-geometry) %>% gather(key="SeverityType", value="Proportion", 2:5)

ggplot(severe, aes(fill = SeverityType, x=Fire_Name, y=Proportion)) + geom_col(position="fill") + coord_flip() + labs(title = "Fires by severity proportions")


```







ACTUAL HOMOGENEITY VALUES IF WANT TO SEE

```{r, echo = FALSE} 

homogeneityGraph <- function(metric) {
  # Make plot
ggplot(fire_df, aes_string(paste("reorder(", "Fire_Name", ", +", metric, ")"), y=metric, fill="Fire_Name")) +
  geom_col() + coord_flip() + theme_minimal() +
  geom_text(aes_string(label = metric), color = "white", hjust=1.3) + labs(title = paste("Fires by", metric, "of severity classes"))

# Save figure to file
# ggsave(filename = (here::here(file.path("figures",paste0(metric,".jpeg")))),
#        width = 7, height = 5)
}


homogeneityGraph('ShannonDiv')
homogeneityGraph('ShannonEven')
homogeneityGraph('PatchDiversity')
homogeneityGraph('EdgeDensity')
```


```{r, include=FALSE, echo=FALSE}
# #Write 
# st_drivers("vector")
# st_write(fire_gjson, here::here(file.path("data","fires_GEDI50_ponderosa.geojson"))) #Write
# sort(unique(fire_gjson$Year))

#firenames <- fire_df %>% as.data.frame() %>% dplyr::select(Fire_ID, Fire_Name) %>% write.csv(here("data", "FireNames.csv"))


```
